Appendix S1

### 2022-06-14 ManuscriptTe.Rmd
Minor Te updates

# APPENDIX S1
We provide an additional example using microclimate data measured along an elevation gradient in CO, USA to illustrate use of TrenchR. We first use a time series of air temperatures and wind speeds collected at multiple heights to examine profiles and surface roughness. We then use a time series of air and surface temperatures, wind speeds, and solar radiation collected at a single height to implement a biophysical model for grasshoppers and compare estimates to observations.

# Microclimate models
```{r, include=FALSE}
setwd("/Volumes/GoogleDrive/Shared drives/TrEnCh/Projects/TrenchR/data/")
C1all=read.csv("microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```

>>>>

# APPENDIX S1
We provide an additional example using microclimate data measured along an elevation gradient in CO, USA to illustrate use of TrenchR. We first use a time series of air temperatures and wind speeds collected at multiple heights to examine profiles and surface roughness. We then use a time series of air and surface temperatures, wind speeds, and solar radiation collected at a single height to implement a biophysical model for grasshoppers and compare estimates to observations. R markdown files with the full code and the associated data are available at https://github.com/trenchproject/TrenchRmanuscript/.

# Microclimate models
```{r, include=FALSE}
C1all=read.csv("./data/microclimate_C1.csv", sep=",", na.strings = c("-49.99","NA"))
```
